Storm surge modelling in the Strait of Georgia

### 2014-10-14 RoughWork/manuscript.tex
Included description of Nov 2009 stats

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 28 cm higher than the modelled residual, however the timing of the surge agrees almost exactly as displayed in Figure \ref{fig:dec2006}. The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 44 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb 4, 2006 case. Error and skill scores for the modelled water level and the modelled residual are provided in Table \ref{tab:dec2006stat}. The modelled residuals are on average too low and have a lower skill score than the Feb 2006 case. This could be due to a number of factors. First,the very large wind speeds observed during this storm are significantly underrepresented by the atmospheric model leading to lower wind stress and less piling of water against the coast. Second, the anomaly forcing at the open boundaries could be too low. The observed residual at Tofino, BC (a point near by but outside of the domain) is up to 10 cm lower than the observed residual at Neah Bay, WA (a point near by but inside of the domain). Since the storm surge is less sensitive to wind forcing at the surface than anomaly forcing at the open boundaries, the latter is likely the case. 
%Skill score between CGRF and observed winds?

@@

The evolution and spatial distribution of the surge is highlighted in Figure \ref{fig:spatial} where the modelled residual is plotted every hour beginning on Dec 15 at 05:30 UTC through to Dec 15 at 14:30 UTC. The surge enters the system from the Strait of Juna de Fuca, peaking between Dec 15 at 9:30 and Dec 15 at 11:30 and then begins to subside throughout the entire domain. Notably, the Strait of Georgia experiences the largest surge values, upwards of 60 cm, whereas the Juan de Fuca region experiences a maximum surge around 45 cm. Additionally, the coastal areas on the mainland side of the Strait of Georgia experience slightly higher surges than the Vancouver Island side, likely due to the southerly wind in the atmospheric model pushing water against the mainland coast. At about 11:30 UTC, the winds switch to northwesterly and then westerly, further amplifying the surge along the mainland coast.

@@

Once again, an evaluation of the model skill for this hindcast is provided in Table \ref{tab:nov2009stat}.

>>>>

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 28 cm higher than the modelled residual, however the timing of the surge agrees almost exactly as displayed in Figure \ref{fig:dec2006}. The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 44 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb 4, 2006 case. Error and skill scores for the modelled water level and the modelled residual are provided in Table \ref{tab:dec2006stat}. All skill scores rank above 0.89. The modelled residuals are on average too low and have a lower skill score than the Feb 2006 case. This could be due to a number of factors. First,the very large wind speeds observed during this storm are significantly underrepresented by the atmospheric model leading to lower wind stress and less piling of water against the coast. Second, the anomaly forcing at the open boundaries could be too low. The observed residual at Tofino, BC (a point near by but outside of the domain) is up to 10 cm lower than the observed residual at Neah Bay, WA (a point near by but inside of the domain). Since the storm surge is less sensitive to wind forcing at the surface than anomaly forcing at the open boundaries, the latter is likely the case. 
%Skill score between CGRF and observed winds?

@@

The evolution and spatial distribution of the surge is highlighted in Figure \ref{fig:spatial} where the modelled residual is plotted every hour beginning on Dec 15 at 05:30 UTC through to Dec 15 at 14:30 UTC. The surge enters the system from the Strait of Juna de Fuca, peaking between Dec 15 at 9:30 and Dec 15 at 11:30 and then begins to subside throughout the entire domain. Notably, the Strait of Georgia experiences the largest surge values, upwards of 60 cm, whereas the Juan de Fuca region experiences a maximum surge around 45 cm. Additionally, the coastal areas on the mainland side of the Strait of Georgia experience slightly higher surges (\~ 10 cm) than the Vancouver Island side, likely due to the southerly wind in the atmospheric model pushing water against the mainland coast. At about 11:30 UTC, the winds switch to northwesterly and then westerly, further amplifying the surge along the mainland coast.

@@

Once again, an evaluation of the model skill for this hindcast is provided in Table \ref{tab:nov2009stat}. The modelled water levels and residuals are too high, except at Victoria. Although Victoria has the smallest mean error in both the water level and residuals, its Willmott skill score and $\gamma^2$ values rank low when compared to the other stations. Generally, the skills scores are very good, scoring above 0.89 at all stations.
